TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2019-06-10 paper/draft.tex
P7_comments
acks

%%==========================================================================================
\acknowledgements
We would like to acknowledge Hans Walter Rix (MPIA), Derek Homeier (Universit{\"a}t Heidelberg), Wolfgang Bradner (MPIA), Anna-Christina Eilers (MPIA), Diogo Souto (Observatário Nacional/MCTI) and Keivan Stassun (Vanderbuilt) for constructive discussions in the process of this project, as well as Bertrand Goldman (MPIA) and those who have supported the internship program at the Max Planck Institute f{\"u}r Astronomie for providing JB with funding and hospitality.

@@

\color{gcolor}{HOGG: grants etc}\color{black}

\color{gcolor}{ADAM: grants etc, FAST acknowledgement?}\color{black}

>>>>

%%==========================================================================================
\acknowledgements
We would like to acknowledge Hans Walter Rix (MPIA), Derek Homeier (Universit{\"a}t Heidelberg), Wolfgang Bradner (MPIA), Anna-Christina Eilers (MPIA), Diogo Souto (Observatário Nacional/MCTI) and Keivan Stassun (Vanderbuilt) for constructive discussions in the process of this project, as well as Bertrand Goldman (MPIA) and those who have supported the internship program at the Max Planck Institute f{\"u}r Astronomie for providing JB with funding and hospitality.
This project was partially supported by
the US National Aeronautics and Space Administration (NASA grant NNX12AI50G),
the US National Science Foundation (NSF grant AST-1517237),
and the Moore--Sloan Data Science Environment at NYU.

@@

\color{gcolor}{ADAM: please add NASA and NSF grants in the parentheses above, and do you have a FAST acknowledgement?}\color{black}
